A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-09-25 faculty.tex
updates

\section{Mentoring Undergraduate Students}
Surprisingly, some of the best research projects I have seen come from undergraduate students.

>>>>

\section{Mentoring Undergraduate Students}
I have mentored a dozen of undergrad students. Most of them did not last long, but some of them did great work. 
Surprisingly, some of the best research projects I have seen come from undergraduate students.
